### 2024-08-25 draft-2/draft-2.tex
repunctuated the previous change to be easier to parse

\vskip-0.5\parskip If the en passant target is {\it n}\ot3 for some {\it n},
there is a white pawn at index {\it n}\ot4. If the en passant target is
{\it n}\ot6 for some {\it n}, there is a black pawn at index {\it n}\ot5.

>>>>

\vskip-0.5\parskip If the en passant target is {\it n}\ot3 for some {\it n},
then the side to move is black, there is a white pawn at index {\it n}\ot4, and
at {\it n}\ot2 and {\it n}\ot3 the board is empty. If the en passant target is
{\it n}\ot6 for some {\it n}, then the side to move is white, there is a black
pawn at index {\it n}\ot5, and at {\it n}\ot6 and {\it n}\ot7 the board is
empty.
